---
title: "WINK taxonomic report"
output: 
  html_document
params:
  n50: NA
  statsData: NA
  brackenData: NA
  db_used: NA
  filter_used: NA
  total_barcodes: NA
  total_reads: NA
  total_bases: NA
  ass_reads: NA
  run_time: NA
---

```{r, include=FALSE}
# 
require(dplyr)
require(DT)
```

<style>
div.blue { background-color:#e6f0ff;}
</style>

*Generated with the [WINK analysis pipeline](https://github.com/angelovangel/wink.git) on `r Sys.time()`*

<div class = "blue">
#### Run summary
</div>

|                |  |
|----------------|--|
| Detected barcodes:    | `r params$total_barcodes` |
| Total bases:          | `r params$total_bases` |
| Total reads:          | `r params$total_reads` |
| Total assigned reads: | `r params$ass_reads` |
| Mean N50:              | `r as.integer(params$n50)` |
| Run time:             | `r params$run_time` |


<div class = "blue">
#### Sequence data per sample
</div>

```{r, include=TRUE, eval=TRUE, echo=FALSE}
df <- params$statsData %>% 
			dplyr::mutate(file = basename(tools::file_path_sans_ext(file)),
										bases = sum_len) %>%
										#bases_h = si_fmt(bases)) %>%
			dplyr::select(file, num_seqs, bases, min_len, max_len, N50, Q20_perc)
		
datatable(df, filter = 'top',
					extensions = 'Buttons', 
					options = list(dom = 'Btp', 
															 buttons = c('copy', 'csv', 'excel')
															 ), 
					rownames = FALSE, 
					class = 'hover row-border') %>%
	DT::formatStyle('num_seqs',
			 								background = styleColorBar(c(0, max(df$num_seqs)), 'skyblue'),
			 								backgroundSize = '95% 70%',
			 								backgroundRepeat = 'no-repeat',
			 								backgroundPosition = 'right') %>%
	DT::formatStyle('bases',
											background = styleColorBar(c(0, max(df$bases)), 'skyblue'),
											backgroundSize = '95% 70%',
											backgroundRepeat = 'no-repeat',
											backgroundPosition = 'right') %>%
	DT::formatStyle('N50',
											background = styleColorBar(c(0, max(df$N50)), 'skyblue'),
											backgroundSize = '95% 70%',
											backgroundRepeat = 'no-repeat',
											backgroundPosition = 'right') 

```

<div class = "blue">
#### Taxonomic assignments and abundance estimation per sample

- abundance data has been filtered at **`r params$filter_used`%**
- kraken2/bracken database used: `r basename(params$db_used)` 

</div>

```{r, include=TRUE, eval=TRUE, echo=FALSE}

taxdb_left = "https://www.ncbi.nlm.nih.gov/Taxonomy/Browser/wwwtax.cgi?mode=Info&id="
taxdb_right = "&lvl=1&lin=s"

df <- params$brackenData %>%
	dplyr::mutate(
				taxonomyID = paste0(taxdb_left, taxonomy_id, taxdb_right), #two-step mutate to build href
				kraken_reads = kraken_assigned_reads,
				bracken_corr_reads = new_est_reads, 
				freq = round(freq*100, 2)
				) %>% 
	#dplyr::filter(name != "unclassified") %>%
	dplyr::mutate(
				taxonomyID = paste0("<a target = '_blank' href='", taxonomyID, "'>", taxonomy_id, "</a>")
				) %>%
	dplyr::select(file, name, taxonomyID, kraken_reads, bracken_corr_reads, freq)

datatable(
  df,
  escape = FALSE,
  selection = "none",
  caption = "Bracken abundance table",
  filter = 'top', 
  rownames = FALSE, 
  class = 'hover row-border',
  extensions = c('Buttons','Select', 'SearchPanes'),
  options = list(dom = 'Prtip', 
  							 buttons = c('copy', 'csv', 'excel'),
  							 searchPanes = list(cascadePanes = TRUE),
  							 columnDefs = list(
  							 	# force search panes to col 1 and 2 only
  							 	list(
  							 		searchPanes = list(show = TRUE), targets = 0:1
  							 		),
  							 	list(
  							 		searchPanes = list(show = FALSE), targets = 2:5
  							 	)
  							 	))
)

```
